---
title: "Wine"
output: html_document
editor_options: 
  chunk_output_type: console
---



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

```



Predicting Wine

GLMNet and TidyLo

```{r}

library(tidyverse)
library(tidytext)
library(glmnet)
library(tidylo)


wine_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-28/winemag-data-130k-v2.csv")


```


We want to use text to make some prediction about whats a good wine. 
Lets start by thinking how we can distinguish what is a good wine.


```{r}

glimpse(wine_ratings)

summary(wine_ratings$points)

wine_ratings %>% 
        ggplot(aes(points)) + 
        geom_histogram() + 
        theme_minimal()

```


```{r}

wine_ratings %>% 
  filter(!is.na(country)) %>%
        ggplot(aes(fct_reorder(country, points), points, 
                   group = country, 
                   color = country)) + 
        geom_boxplot() + 
        theme_minimal() +
        guides(color = FALSE) + 
        coord_flip()

```


```{r}

most_common_wines <- wine_ratings %>% 
  filter(!is.na(variety)) %>%
  group_by(variety) %>% 
  summarise(reviews = n()) %>% 
  ungroup() %>%
  top_n(10, wt = reviews) 


most_common_wines %>% 
  left_join(wine_ratings, by = 'variety') %>% 
  ggplot(aes(fct_reorder(variety, points), points, 
                   group = variety, 
                   color = variety)) + 
        geom_boxplot() + 
        theme_minimal() +
        guides(color = FALSE) + 
        coord_flip()

```



### Tidy Lo


Lets take a minute to look at Julia Silge's tidy lo package to help explore some of our text data. 
So specifically, we want to know; what are the highest log odds terms for these wine varieties?

```{r}


wine_text <- wine_ratings %>% 
        unnest_tokens(ngram, description, token = "ngrams", n = 1)


wine_log_odds <- wine_text %>%
        count(ngram, variety) %>%
        bind_log_odds(variety, ngram, n)


variety_list <- wine_text %>% 
  select(variety) %>% 
  distinct() %>%
  unnest_tokens(var_gram, variety, token = stringr::str_split, pattern = " ") %>%
  mutate(var_gram = tolower(var_gram), 
         var_gram = str_trim(var_gram, side = 'both')) %>%
  pull(var_gram)


wine_stops <- c(
  "cabernet", "bordeaux", "merlot", "sauvignon", "chardonnay", "merlot's", 
  "merlots", "pinot", "pinots", "sauvignon", "syrah", "syrahs", "blend", 
  "riesling", "noir", "rosé", "chablis", "sirah", "cab", "sample", "sb"
)
  
```


What we're looking for here is to see the difference between using TF-IDF and Log odds for selecting the most 'important' words for some these wine descriptions. 

So after cleaning up our log odds by removing overly-obvious words (i.e. the names of wine varieties), how well do these top ten key words work for each wine variety. 

The results are pretty good. 
I'm not a wine drinker, but these log odds selected words make the wines sound delicious. 

By describing a Chardonnay as buttered, pineapple, chard, pear, toast, tropical, lemon ... I'm getting a really nice description that doesn't sound anything like one of the other varieties. 
Cola, cranbrerry, chery, silky, raspberry, tea ... is painting a very different description. 


```{r}

most_common_wines %>% 
  left_join(wine_log_odds, by = 'variety') %>% 
  mutate(ngram = str_replace(ngram, '\\d+', '')) %>%
  filter(ngram != '') %>%
  filter(!ngram %in% variety_list) %>%
  filter(!ngram %in% wine_stops) %>%
  group_by(variety) %>% 
  top_n(10, wt = log_odds) %>%
  ungroup() %>%
  mutate(variety = as.factor(variety),
         ngram = reorder_within(ngram, log_odds, variety)) %>%
  ggplot(aes(ngram, log_odds)) + 
  geom_col() + 
  coord_flip() + 
  scale_x_reordered() +
  facet_wrap(~variety, scales = 'free') + 
  theme_minimal()

```



### Topic Modeling



```{r}

library(tidytext)
library(textmineR)
library(rsample)

variety_list <- wine_text %>% 
  group_by(variety) %>% 
  summarise(articles = n()) %>%
  top_n(20, wt = articles) %>%
  pull(variety)



df <- wine_ratings %>% 
  filter(variety %in% variety_list)


split <- initial_split(df, prop = .75)
train <- training(split)
test <- testing(split)



# tokenize using tidytext's unnest_tokens
tidy_wine <- train %>% 
  unnest_tokens(output = ngram, 
                input = description,
                stopwords = c(stopwords::stopwords("en"), 
                              stopwords::stopwords(source = "smart"), 
                              variety_list, 
                              wine_stops),
                token = "ngrams",
                n_min = 1, n = 2) %>% 
  count(variety, ngram) %>% 
  filter(n > 1) #Filtering for words/bigrams per document, rather than per corpus

tidy_wine <- tidy_wine %>% # filter words that are just numbers
  filter(! stringr::str_detect(tidy_wine$ngram, "^[0-9]+$"))

# turn a tidy tbl into a sparse dgCMatrix for use in textmineR
d <- tidy_wine %>% 
  cast_sparse(variety, ngram, n)


# create a topic model
m <- FitLdaModel(dtm = d, 
                 k = 20,
                 iterations = 200,
                 burnin = 175)



# below is equivalent to tidy_beta <- tidy(x = m, matrix = "beta")
tidy_beta <- data.frame(topic = as.integer(stringr::str_replace_all(rownames(m$phi), "t_", "")), 
                        m$phi, 
                        stringsAsFactors = FALSE) %>%
  pivot_longer(
    -topic, 
    names_to = 'term', 
    values_to = 'beta') %>% 
  tibble::as_tibble() %>% 
  mutate(term = str_replace(term, '.', ' '))

# below is equivalent to tidy_gamma <- tidy(x = m, matrix = "gamma")
tidy_gamma <- data.frame(document = rownames(m$theta),
                         m$theta,
                         stringsAsFactors = FALSE) %>%
  pivot_longer(
    -document, 
    names_to = 'topic',  
    values_to = 'gamma')



  
```

